---
title: "data_aggregation"
output: html_document
date: "2023-02-15"
---

## Cleaning environment

```{r}
rm(list=ls())
```

```{r}
# Load packages
install.packages("tidyverse")
library(tidyverse)
```

```{r}
install.packages("lubridate")
library(lubridate)
```
# Turbine Aggregation
## Importing the turbine data

```{r}
all_turbine = read.csv(file.choose(),header=T)
```

## Making the column time_interval a time object

```{r }
# R doesn't know start_date and end_date are dates - they were read in as numeric
# convert those both to date objects
all_turbine$Time = ymd_hms(all_turbine$Time)
```

## Rounding the time_interval column to "10 minutes"

```{r}
all_turbine$interval_time = round_date(all_turbine$Time, "10 mins")
```

## Writing all_turbine data to a csv file
```{r}
# Writing all_turbine data to a csv file
write_csv(all_turbine, path = "all_turbine.csv")
```


# WindSpeed Aggregation
## Importing the WindSpeed data

```{r}
All_windspeed = read.csv(file.choose(),header=T)
```

## Making the column time_interval a time object

```{r }
# R doesn't know start_date and end_date are dates - they were read in as numeric
# convert those both to date objects
All_windspeed$TimeStamp = ymd_hms(All_windspeed$TimeStamp)
```

## Rounding the time_interval column to "10 minutes"
```{r}
All_windspeed$interval_time = round_date(All_windspeed$TimeStamp, "10 mins")
```

## Writing All_windspeed data to a csv file
```{r}
# Writing all_generator_rpm data to a csv file
write_csv(All_windspeed, file = "/Users/gonzalovaldenebro/Library/CloudStorage/OneDrive-DrakeUniversity/STAT 190/Project 1/Data/All_windspeed.csv")
```


# Generator RPM Aggregation
## Importing the WindSpeed data
```{r}
all_generator_rpm = read.csv(file.choose(),header=T)
```

## Making the column time_interval a time object
```{r }
# R doesn't know start_date and end_date are dates - they were read in as numeric
# convert those both to date objects
all_generator_rpm$TimeStamp = ymd_hms(all_generator_rpm$TimeStamp)
```

## Rounding the time_interval column to "10 minutes"
```{r}
all_generator_rpm$interval_time = round_date(all_generator_rpm$TimeStamp, "10 mins")
```

## Writing all_turbine data to a csv file
```{r}
# Writing all_generator_rpm data to a csv file
write_csv(all_generator_rpm, file = "/Users/gonzalovaldenebro/Library/CloudStorage/OneDrive-DrakeUniversity/STAT 190/Project 1/Data/all_generator_rpm.csv")
```

